---
title: "My answers"
author: "My name"
output: html_document
---


## Instructions

Solutions will be turned in via GitHub Classroom.
**Only most recent commit on the main branch when the assignment is due will be graded**.
Your solution must use the `Rmarkdown` template provided in the assignment's repository that you cloned for this assignment. 
This means your answers will be compiled into a file called `assignment_answers.pdf`.
Failure to follow these steps and submit `assignment_answers.pdf` in your GitHub repository along with the `assignment_answers.Rmd`, will result in a assignment grade of **zero**.
Refer to the repository's `README.md` for instructions on how to complete the title and author fields for submission.

Each group has been assigned a **group leader**.
It is the group leaders job to "accept" the assignment via GitHub and then add all group members as collaborators to the group assignment. 
To do this, the group leader will need each member's GitHub username.
The group leader can add group members as follows:

- Go to their group assignment repository on GitHub
- Click on the Settings tab
- Go to 'Manage Access'
- Click on 'Invite teams or people'
- Enter the GitHub usernames of each group member, one by one, and give them 'Write' access
- Click 'Add <username> to this repository'

Group members will then get an email to accept this invitation.
Group members **must accept** this invitation to be able to view and contribute to the assignment.

To work on this assignment, first clone the GitHub repository to your machine, see the `README.md` for more details.
After you have cloned the repository to your machine, you can access the data for this assignment.
Open an RStudio session and use this folder as a project.
The data is located in the `data` sub-directory.
Be sure to install all the necessary packages so that your solution document will run from start to finish.

Remember, your goal is to communicate. 
Full credit will be given only to the correct solution which is described and/or coded clearly. 
Convoluted and obtuse descriptions/code might receive low marks, even when they are correct. 
Aim for concise solutions, as it will save you time spent on write-ups, and also help you conceptualize the key ideas you are trying to express.
Sentence limits often apply to questions that require written answers - stick to them (or under them) to get full credit.

## Context: Experiments with Advertising Effectiveness

Suppose you are working at a marketing consultancy as a team of marketing analysts in the newly established (though fictitious) country of Petersville.
Petersville is a large geographically, and is divided into 100 geographical areas, known as "Designated Market Areas" or DMAs.
Each DMA shares common, localized, market conditions but may differ in population size.
The citizens are generally "low mobility", meaning they rarely travel beyond the DMA they reside in, except for 10% of citizens who commute long distances into different DMAs for work.
Furthermore, Petersville has strict privacy regulations which prevents experiments from being conducted at the unit of individual citizens by either the government or firms that operate in country.

Your latest project involves studying the effectiveness of online advertising by the largest company in Petersville.
The digital environment in Petersville can be thought of as a simplified version of what we live in and experience today.
There is one search engine for the internet which serves online advertising as part of the search results.
There are no other online advertising opportunities.
The company has approached you because it wants to start using online advertising for the first time.
In particular, they want to know whether online advertising increases consumer spending and whether it yields a positive return on investment.

For this exercise you might need to use the following packages:

```{r, warning= FALSE, message=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(vtable)
library(broom)
library(tidyr)
library(purrr)
library(rsample)
```

Install them if you have not done so already.

### Part 1: Experiment Design (5 points)

1. [3 points] In the meeting where your team begins to discuss how to design the experiment, a colleague suggested the following:

> Let's start advertising in the largest DMAs first and see if sales increase. If they do, we can roll out advertising across all DMAs.

Does your colleagues proposed experiment design lead to an unbiased estimate of the average treatment effect of digital advertising? Explain why or why not. (max. 3 sentences)

Write your answer here


The final experiment that your team decide to implement randomizes using geography. That is, some DMAs (the *treatment* markets) will have online advertising introduced and people who search from these locations see the ads, whereas other DMAs (*the control* markets) will remain with no online advertising meaning that people who search from these locations do not see any ads. Outcome variables will be aggregated to the geographic region.

2. [2 points] List and explain two potential shortcomings of the geography based randomization into a treatment. (max. 2 sentences)

Write your answer here


### Part 2: Essential A/B Test Analytics (15 points)

3. [1 points] The data from the experiment are located in the `data/` directory. Load the data and name it `ad_experiment`. The columns in the data are as follows:

* **`geo`**: An identifier for each DMA.
* **`treatment_status`**: Is the DMA part of the treatment or control group.
* **`test_period`**: Is the point in time before the experiment begins, during the experiment or after it has concluded.
* **`date`**: The calendar date.
* **`sales`**: The amount of sales in dollars earned by the company on a given calendar day.
* **`cost`**: The amount of money spent on online advertising on a given calendar day.

```{r}
# Write your answer here
```


4. [2 points] Evaluate whether the randomization into treatment and control groups by geographic area was successful. Discuss your result. (max. 1 sentence)

```{r}
# Write your answer here
```



5. [1 points] Using data from the test period, compute the average sales and average cost of advertising over the duration of the experiment for the treatment and control groups. 
Also compute the standard error for the sales. Store the data in a dataset named `ad_test_period`. 

```{r}
# Write your answer here
```


6. [1 points] Create a plot that shows the difference in total sales between treatments. Include the error bars in your plot.

```{r}
# Write your answer here
```


7. [1 points] Write down a linear regression equation that allows you to estimate the average treatment effect of advertising on sales, where the "average" is taken over geographical areas. 

```{block}

$$
sales_i = \beta_0 + \beta_1 Treatment_i + \varepsilon_i
$$

```

8. [2 points] Estimate the linear regression you outlined above and report the results.

```{r}
# Write your answer here
```


9. [2 points] What is the average treatment effect of advertising on sales in your data? Is it statistically significant? (max. 2 sentences)

# Write your answer here



10. [3 points] After seeing these results, your manager struggles with interpreting the magnitude of the effect. They suggest that you find an alternate way to report the your estimate. (max. 4 sentences)
    (i) Justify what alternative you will choose,
    (ii) Write the necessary code to obtain the estimate, and
    (iii) Interpret the result.

```{r}
# Write your answer here
```



11. [2 points] While undertaking the analysis, during a discussion over lunch a colleague from a different team suggests:

> If you have data from weeks after the experiment, you should include that in your analysis too.

Explain why they might have made that suggestion, and report the results of making this change to the data included in your analysis. Do your conclusions change? (max. 3 sentences)

```{r}
Write your answer here
```

### Part 3: CUPED (10 points)

After seeing the results from your preliminary analysis, one of the senior members of the team suggest you should adopt the CUPED approach.
In particular they suggest using total sales in the pre-test period as the variable included from pre-existing data.

12. [5 points] Explain intuitively what CUPED does, and propose a pre-existing variable that is in the data which can be used in your analysis. (max 4. sentences)

Write your answer here


13. [4 points] Report an estimate of the treatment effect using CUPED. Again, make sure the magnitude is easily interpretable by a manager.

TIP: Print your estimate of $\theta$ so that if you make a mistake, we can award partial credit.

```{r, solution}
# Write your answer here
```

14. [1 point] Interpret your CUPED estimate and evaluate whether the advertising campaign increases sales based on the estimate. (max. 2 sentences)

```{r}
# Write your answer here
```


### Part 3: Return on Investment [10 points]

The next step in your analysis involves analyzing whether digital advertising should be adopted across all markets for this company. To do this, you need a metric that weighs up the return on investment of advertising spending (ROAS).
Mathematically:

$$
\text{ROAS} = \frac{\text{incremental revenue}}{\text{incremental cost}} = \frac{E(\Delta R)}{E(\Delta C)}
$$

15. [3 points] Compute and report an estimate of ROAS. Interpret your estimate. (max. 2 sentences)

```{r}
# Write your answer here
```

16.  [7 points, **Challenging**] To evaluate whether your estimate of ROAS is statistically significant, you want to construct a confidence interval for this estimate. 
    (i) [5 points, challenging] Construct a 95% confidence interval for the ROAS.
    (ii) [2 points] Draw a conclusion about whether advertising experiment has a positive ROAS. (max. 2 sentences)

HINT: There may be more than one correct way to do this. We recommend thinking about how you can re-sample data many times to compute a distribution of ROAS.

```{r}
# Write your answer here
```


## Part 4: Summary & Managerial Implications (10 points)

17. [10 points] Using all of the answers and analysis you have performed so far, write a "Management
Summary" that details the research question, relevance, outlines the experiment performed,
summarises the main findings and provides a managerial recommendation. 

You have a maximum of two paragraphs with at most 12 total sentences to write this summary.^[ 
    Think of this summary as the first thing that will be read by managers and analysts who are
attending a meeting that you will lead which reports on the experiment conducted.
The meeting would be run as follows: (i) There are no slides or Powerpoint presentations, (ii) for the
first 15 mins of the meeting all participants read a four page narrative memo summarising the
experiment and the results of which your Management Summary is the first page, (iii) After reading
the report, the meeting will continue and attendees will be able to ask your team further questions to
develop a deeper understanding of what you have done.
    Use the tips from the document "Write like an Amazonian" that we have posted on the course website.
These tips are written to help staff at Amazon write concise and meaningful documents, and are
helpful to ensure your writing gets to the point.
]


Write your answer here

